Binary companions of red clump stars

### 2017-08-04 paper/main.tex
authors
equations of pain

% adjust AAS-TEX shit
\setlength{\parindent}{1.\baselineskip}

@@

\author{David~W.~Hogg}
\affiliation{Center for Cosmology and Particle Physics,
             Department of Physics,
             New York University, 726 Broadway,
             New York, NY 10003, USA}
\affiliation{Max-Planck-Institut f\"ur Astronomie,
             K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\affiliation{Flatiron Institute,
             Simons Foundation,
             162 Fifth Avenue,
             New York, NY 10010, USA}

@@

@@

APW: Opening sentence: If we see RV changes, there must be binaries!
Can we infer binary populations from bad data?

@@

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function. We hereby
  take on all the assumptions given in \sectionname~\ref{sec:fitting},
  about noise and kinematics, and so on.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[population parameterization] whatevs
\end{description}

>>>>

% adjust AAS-TEX shit
\setlength{\parindent}{1.1\baselineskip}

@@

\author[0000-0003-2866-9403]{David~W.~Hogg}
\affiliation{Max-Planck-Institut f\"ur Astronomie,
             K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\affiliation{Center for Cosmology and Particle Physics,
             Department of Physics,
             New York University, 726 Broadway,
             New York, NY 10003, USA}
\affiliation{Center for Data Science,
             New York University, 60 Fifth Ave,
             New York, NY 10011, USA}
\affiliation{Flatiron Institute,
             Simons Foundation,
             162 Fifth Avenue,
             New York, NY 10010, USA}

@@

\author{Jason~Cao}
\affiliation{Center for Cosmology and Particle Physics,
             Department of Physics,
             New York University, 726 Broadway,
             New York, NY 10003, USA}

@@

APW: Opening sentence: Even with one single star and two epochs, if we
see an RV change, there must be binaries! What more can we say? Can we
infer binary populations from bad data?

@@

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function. We hereby
  take on all the assumptions given in \sectionname~\ref{sec:fitting},
  about noise and kinematics, and so on.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[masses known] The mass of each primary \RC\ star is known, with
  a correctly known posterior pdf, from prior work (CITE NESS).
\item[population parameterization] We adopt the following
  parameterization of the population. In what follows, $\theta$ will
  stand in for the full set of hyper-parameters (population
  parameters).
  \begin{itemize}
  \item Each primary \RC\ star has a probability $F$ (pure probability
    $0<F<1$) of having a secondary companion. $F$ is a hyper-parameter
    in $\theta$.
  \item The log-period distribution $p(\ln P\given\theta)$ is a power
    law between end-points, or
    \begin{eqnarray}
      \ln p(\ln P\given\theta) &=& g_0 + (g_1 - g_0)\,\frac{\ln P - x_0}{x_1 - x_0}
      \quad \mbox{for $x_0<\ln P<x_1$,}
    \end{eqnarray}
    where $g_0, g_1, x_0, x_1$ are hyper-parameters in $\theta$.
  \item Each primary star has a true mass $M$ (which we only know
    noisily) and the companion mass is potentially larger or
    smaller (!). The log-mass-ratio distribution $p(\ln q\given\theta)$ is
    \begin{eqnarray}
      \ln p(\ln q\given\theta) &=& h_0 + (h_1 - h_0)\,\frac{\ln q - y_0}{y_1 - y_0}
      \quad \mbox{for $y_0<\ln q<y_1$,}
    \end{eqnarray}
    where $h_0, h_1, y_0, y_1$ are hyper-parameters in $\theta$.
  \item The eccentricity distribution $p(e\given P,\theta)$ is a beta,
    and permitted to vary with period:
    \begin{eqnarray}
      p(e\given P,\theta) &=& B(e\given \alpha(P),\beta(P))
      \\
      \alpha(P) &=& a_0 + (a_1 - a_0)\,\frac{P - x_0}{x_1 - x_0}
      \\
      \beta(P) &=& b_0 + (b_1 - b_0)\,\frac{P - x_0}{x_1 - x_0}
      \quad ,
    \end{eqnarray}
    where $B(x\given\alpha,\beta)$ is the beta distribution with
    control parameters $\alpha,\beta$, and $a_0, a_1, b_0, b_1$ are
    hyper-parameters in $\theta$.
  \item The inclination distribution $p(i)$ and the argument-of-perihelion
    distribution $p(\omega)$ and the phase distribution $p(\phi)$ are all
    fixed to their isotropic distributions. They bring no hyper-parameters
    to $\theta$.
  \end{itemize}
\item[hyper-priors] whatevs
\end{description}
